---
title: "Wasmbounds results"
author: "Raven Szewczyk"
date: "2022-07-11"
output:
  html_document:
    toc: yes
  pdf_document:
    toc: yes
params:
  machine_name: "kone"
---

```{r setup, include=FALSE, error=FALSE}
library(tidyverse)
library(rio)
library(scales)
library(xtable)
library(ggbreak)
library(patchwork)
knitr::opts_chunk$set(echo = FALSE, error = TRUE)
```

```{r read_raw_csv, include=FALSE, error=FALSE}
machine <- params$machine_name
raw_csv <- import(paste0("../runs/", machine, ".csv"), "csv", fill=TRUE, header=TRUE)
```

```{r parse_csv, include=FALSE, error=FALSE}

t_us <- raw_csv %>%
    select(benchid, runid, starts_with("mus_")) %>%
    pivot_longer(cols = starts_with("mus_"), names_to = c("mid"), names_pattern="mus_([0-9]+)", values_to = c("us"), values_drop_na = TRUE)

t_us_stats <- t_us %>% select(runid,us) %>%
    group_by(runid) %>%
    arrange(us) %>%
    summarise(mean_us=mean(us), med_us=median(us),
        min_us=quantile(us, 0.01), max_us=quantile(us, 0.99), num_us=n(),
        q1_us=quantile(us, 0.25), q3_us=quantile(us, 0.75))

LBL_NATIVE_GCC <- 'Native\nGCC'
LBL_NATIVE_CLANG <- 'Native\nClang'

t_info <- raw_csv %>% select(!starts_with("mus_") & !starts_with("local_io") & !starts_with("local_net") & !starts_with("local_faasm")) %>% filter(nthreads != 32) %>%
  mutate (
    benchname = factor(benchname),
    runner = factor(runner, ordered = TRUE,
      levels = c("native.gcc", "native.clang", "wavm.wasm", "wasmtime.wasm", "wasm3.wasm", "nodejs.wasm"),
      labels = c(LBL_NATIVE_GCC, LBL_NATIVE_CLANG, "WAVM", "Wasmtime", "W3", "V8")
    ),
    nthreads_f = factor(nthreads),
    bounds = factor(
      ifelse(as.character(runner) == "W3", "trap", as.character(bounds))
      , ordered = TRUE,
      levels = c("none",      "mdiscard", "uffd", "clamp",          "trap"),
      labels = c("No checks", "Mprotect", "UFFD", "Clamp", "Trap")),
    default_bounds_name = ifelse(startsWith(as.character(runner), "Native"), "No checks", ifelse(as.character(runner) == "W3", "Trap", "Mprotect")),
    is_default_bounds = as.character(bounds) == as.character(default_bounds_name),
    runbounds = factor(paste(runner, bounds, sep = "\n")),
    suite = factor(ifelse(startsWith(as.character(benchname), "rundirs"), "SPEC", "PBC")),
    suite_fancy = factor(ifelse(startsWith(as.character(benchname), "rundirs"), "SPEC CPU", "PolyBench/C")),
    benchname_fancy = str_match(as.character(benchname), "^(rundirs/[0-9]+\\.)?([^_]+)")[,3]
  ) %>%
  left_join(t_us_stats)

if ("local_cpums_user_sum" %in% names(t_info)) {
  t_info <- mutate(t_info, total_cpums = local_cpums_user_sum + local_cpums_nice_sum + local_cpums_system_sum + local_cpums_idle_sum + local_cpums_irq_sum + local_cpums_softirq_sum)
}

gcc_times <- t_info %>% filter(runner == LBL_NATIVE_GCC) %>% select(benchid, nthreads, gcc_us = med_us)
clang_times <- t_info %>% filter(runner == LBL_NATIVE_CLANG) %>% select(benchid, nthreads, clang_us = med_us)
clang_1t_times <- t_info %>% filter(runner == LBL_NATIVE_CLANG, nthreads == 1) %>% select(benchid, clang_1t_us = med_us)

t_info <- left_join(t_info, gcc_times, by = c('benchid', 'nthreads'))
t_info <- left_join(t_info, clang_times, by = c('benchid', 'nthreads'))
t_info <- left_join(t_info, clang_1t_times, by = c('benchid'))

usms <- 1.0/1000.0
uss <- usms/1000.0

paper_plot_w <- 8
paper_plot_w_narrow <- 4
paper_plot_h <- 4
paper_plot_h_narrow <- 3
paper_font <- "serif"
paper_pointsize <- 10
paper_theme <- theme_light() +
  theme(
    plot.title=element_blank(),
    legend.margin=margin(0,0,0,0,"cm"),
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
    strip.background = element_rect(fill = "#eeeeee", colour = "#aaaaaa"),
    strip.text = element_text(colour = "#000000")
  )
set1_scale <- brewer_pal(palette="Set1")(24)
set1_scale[6] <- "#3c009c"
paper_disc_scale <- scale_color_manual(values = set1_scale)
paper_fill_scale <- scale_fill_manual(values = set1_scale)
paper_shape_scale <- scale_shape_manual(values = c(0,1,2,3,4,5,6,14))

paper_plot_path <- paste0('plots/wasmbounds_', machine, '_')

if (!dir.exists("plots")) {
  dir.create("plots")
}

gplt <- NULL
oplt <- NULL

has_16t <- (max(t_info$nthreads) >= 16)
```

## Timing

### Relative vs Native-Clang
#### 1 Thread
```{r latency_rel_1t_motivation}
# ymin = latency_us_q1*plot_scale, , ymax = latency_us_q3*plot_scale
gplt <- ggplot(t_info %>% filter(benchname != 'noopbench', nthreads == 1, bounds == "Mprotect" | bounds == "No checks", runner == "V8"),
    aes(x = benchname_fancy, group = runbounds, fill = bounds)) +
  facet_grid(~suite_fancy, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  theme(legend.position = "top") +
  geom_col(aes(y = med_us / clang_us), position='dodge2') +
  geom_hline(aes(yintercept = 0.0)) +
  # scale_y_continuous(breaks = pretty_breaks(n=10)) +
  labs(fill = "V8 Bounds checking") +
  xlab("Benchmark") + ylab("Time vs native (Lower=Better)")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "latency_relative_motivation_v8.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

```{r latency_rel_1t}
# ymin = latency_us_q1*plot_scale, , ymax = latency_us_q3*plot_scale
gplt <- ggplot(t_info %>% filter(benchname != 'noopbench', nthreads == 1),
    aes(x = benchname, group = runbounds, fill = runner, colour = bounds)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = med_us / clang_us - 1), position='dodge') +
  geom_errorbar(aes(ymax = q3_us / clang_us - 1, ymin = q1_us / clang_us - 1), position='dodge') +
  geom_hline(aes(yintercept = 0.0)) +
  scale_y_continuous(breaks = pretty_breaks(n=10)) +
  labs(title = "Relative slowdown (Lower is better)", fill = "VM", colour = "Bounds\nchecking") +
  xlab("Benchmark") + ylab("Relative slowdown (Lower=Better)")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "latency_relative_1thread.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

#### 16 Threads
```{r latency_rel_16t, eval=has_16t}
gplt <- ggplot(t_info %>% filter(benchname != 'noopbench', nthreads == 16),
    aes(x = benchname, group = runbounds, fill = runner, colour = bounds)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = med_us / clang_us - 1), position='dodge') +
  geom_errorbar(aes(ymax = q3_us / clang_us - 1, ymin = q1_us / clang_us - 1), position='dodge') +
  geom_hline(aes(yintercept = 0.0)) +
  scale_y_continuous(breaks = pretty_breaks(n=10)) +
  labs(title = "Relative slowdown (Lower is better)", fill = "VM", colour = "Bounds\nchecking") +
  xlab("Benchmark") + ylab("Relative slowdown (Lower=Better)")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "latency_relative_16thread.pdf"), width=24, height=6, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

#### Default bounds
```{r latency_rel_1t_defbounds}
# ymin = latency_us_q1*plot_scale, , ymax = latency_us_q3*plot_scale
gplt <- ggplot(t_info %>% filter(benchname != 'noopbench', nthreads == 1, is_default_bounds),
    aes(x = benchname, group = runbounds, fill = runner)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = med_us / clang_us - 1), position='dodge2') +
  geom_errorbar(aes(ymax = q3_us / clang_us - 1, ymin = q1_us / clang_us - 1), position = position_dodge2(width = 0.5, padding = 0.5)) +
  geom_hline(aes(yintercept = 0.0)) +
  scale_y_continuous(breaks = pretty_breaks(n=10)) +
  labs(title = "Relative slowdown (Lower is better)", fill = "VM", colour = "Bounds\nchecking") +
  xlab("Benchmark") + ylab("Relative slowdown (Lower=Better)")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "latency_relative_1thread_defbounds.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

#### Default bounds excluding wasm3
```{r latency_rel_1t_defbounds_no_w3}
# ymin = latency_us_q1*plot_scale, , ymax = latency_us_q3*plot_scale
gplt <- ggplot(t_info %>% filter(benchname != 'noopbench', nthreads == 1, runner != 'W3', is_default_bounds),
    aes(x = benchname, group = runbounds, fill = runner)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = med_us / clang_us - 1), position='dodge2') +
  geom_errorbar(aes(ymax = q3_us / clang_us - 1, ymin = q1_us / clang_us - 1), position = position_dodge2(width = 0.5, padding = 0.5)) +
  geom_hline(aes(yintercept = 0.0)) +
  scale_y_continuous(breaks = pretty_breaks(n=10)) +
  labs(title = "Relative slowdown (Lower is better)", fill = "VM", colour = "Bounds\nchecking") +
  xlab("Benchmark") + ylab("Relative slowdown (Lower=Better)")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "latency_relative_1thread_defbounds_no_w3.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

#### Default bounds excluding wasm3 - absolute values
```{r latency_rel_1t_defbounds_no_w3_abs}
gplt <- ggplot(t_info %>% filter(benchname != 'noopbench', nthreads == 1, runner != 'W3', bounds != 'Trap', bounds != 'Clamp', bounds != 'UFFD', (bounds != 'No checks') | (runner == LBL_NATIVE_CLANG) | (runner == LBL_NATIVE_GCC)),
    aes(x = benchname, group = runbounds, fill = runner)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = med_us), position='dodge2') +
  geom_errorbar(aes(ymax = q3_us, ymin = q1_us), position = position_dodge2(width = 0.5, padding = 0.5)) +
  geom_hline(aes(yintercept = 0.0)) +
  scale_y_log10(breaks = log_breaks(n=10)) +
  labs(title = "Microseconds", fill = "VM", colour = "Bounds\nchecking") +
  xlab("Benchmark") + ylab("Microseconds")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "latency_absolute_1thread_defbounds_no_w3.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```


```{r latency_rel_1t_defbounds_no_w3_abs_uffd}
gplt <- ggplot(t_info %>% filter(benchname != 'noopbench', nthreads == 1, runner != 'W3', (bounds == 'UFFD') | (bounds == 'mprotect')),
    aes(x = benchname, group = runbounds, fill = runner, color = bounds)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = med_us), position='dodge2') +
  geom_errorbar(aes(ymax = q3_us, ymin = q1_us), position = position_dodge2(width = 0.5, padding = 0.5)) +
  geom_hline(aes(yintercept = 0.0)) +
  scale_y_log10(breaks = log_breaks(n=10)) +
  labs(title = "Microseconds", fill = "VM", colour = "Bounds\nchecking") +
  xlab("Benchmark") + ylab("Microseconds")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "latency_absolute_1thread_defbounds_no_w3_uffd.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

```{r latency_rel_16t_defbounds_no_w3, eval=has_16t}
gplt <- ggplot(t_info %>% filter(benchname != 'noopbench', nthreads == 16, runner != 'W3', bounds != 'Trap', bounds != 'Clamp', bounds != 'UFFD', (bounds != 'No checks') | (runner == LBL_NATIVE_CLANG) | (runner == LBL_NATIVE_GCC)),
    aes(x = benchname, group = runbounds, fill = runner)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = med_us), position='dodge2') +
  geom_errorbar(aes(ymax = q3_us, ymin = q1_us), position = position_dodge2(width = 0.5, padding = 0.5)) +
  geom_hline(aes(yintercept = 0.0)) +
  scale_y_log10(breaks = log_breaks(n=10)) +
  labs(title = "Microseconds", fill = "VM", colour = "Bounds\nchecking") +
  xlab("Benchmark") + ylab("Microseconds")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "latency_absolute_16thread_defbounds_no_w3.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

### Method comparison (geom avg)
#### 1 Thread Compact Motivation
```{r latency_rel_method_1t_motivation, eval=has_16t}
method_stats <- t_info %>% filter(benchname != 'noopbench', nthreads == 16, bounds == "Mprotect" | bounds == "No checks") %>%
  group_by(runner, bounds, suite) %>% summarise(
    slowdown = exp(mean(log(med_us / clang_us), na.rm = TRUE))
  )
stats_breaks = sort(method_stats$slowdown, decreasing=TRUE)
gplt <- ggplot(method_stats,
    aes(x = suite, fill = bounds, group = bounds, y = slowdown)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  theme(legend.position = "top") +
  geom_col(position='dodge2', show.legend = TRUE) +
  geom_hline(aes(yintercept = 1.0), linetype = "dashed", col = "#444444") +
  scale_y_continuous(breaks = pretty_breaks(), expand=c(0.1, 0)) +
  labs(fill = "Bounds checking mechanism") +
  xlab("Benchmark") + ylab("Relative time (Lower=Better)")

if (!is.null(gplt)) {
  ggsave(paste0(paper_plot_path, "geomean_slowdown_motivation.pdf"), plot = gplt, onefile = FALSE, width=6, height=4, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
}
oplt <- gplt
gplt <- NULL
oplt
```

#### 1 Thread
```{r latency_rel_method_1t}
method_stats <- t_info %>% filter(benchname != 'noopbench', nthreads == 1) %>%
  group_by(runner, bounds, suite) %>% summarise(
    slowdown = exp(mean(log(med_us / clang_us), na.rm = TRUE))
  )
stats_breaks = sort(method_stats$slowdown, decreasing=TRUE)
gplt <- ggplot(method_stats,
    aes(x = interaction(suite, bounds), fill = bounds, group = bounds, y = slowdown)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  theme(strip.text.x = element_text(size = 6), strip.text.y = element_text(size = 5)) +
  geom_col(position='dodge', show.legend = FALSE) +
  geom_text(aes(label = sprintf("%.0f%%", slowdown*100), y = pmax(slowdown, 1)), size = 3, hjust = -0.1, vjust = 0.5, angle = 90, show.legend = FALSE) +
  geom_hline(aes(yintercept = 1.0), linetype = "dashed", col = "#444444") +
  scale_y_continuous(breaks = pretty_breaks(), expand=c(0.1, 0)) +
  scale_y_break(c(stats_breaks[2] + 0.1, stats_breaks[1] - 0.3),
      scales = 0.25, expand = expansion(add = c(0, 0.7)),
      ticklabels = c(signif(stats_breaks[1], digits = 2))) +
  labs(title = "Relative time (Lower is better)") +
  xlab("Benchmark") + ylab("Relative time (Lower=Better)")

if (!is.null(gplt)) {
  width <- 6
  if (machine == "riscv") {
    width <- 3
  }
  ggsave(paste0(paper_plot_path, "geomean_slowdown_1thread.pdf"), plot = gplt, onefile = FALSE, width=width, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
}
oplt <- gplt
gplt <- NULL
oplt
```

#### 16 Threads
```{r latency_rel_method_16t, eval=has_16t}
method_stats <- t_info %>% filter(benchname != 'noopbench', nthreads == 16) %>%
  group_by(runner, bounds, suite) %>% summarise(
    slowdown = exp(mean(log(med_us / clang_us), na.rm = TRUE))
  )
stats_breaks = sort(method_stats$slowdown, decreasing=TRUE)
gplt <- ggplot(method_stats,
    aes(x = interaction(suite, bounds), fill = bounds, group = bounds, y = slowdown)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(position='dodge', show.legend = FALSE) +
  geom_text(aes(label = sprintf("%.2f%%", slowdown*100), y = pmax(slowdown, 1)), size = 2, hjust = 0.5, vjust = -0.5, show.legend = FALSE) +
  geom_hline(aes(yintercept = 1.0), linetype = "dashed", col = "#444444") +
  scale_y_continuous(breaks = pretty_breaks(), expand=c(0.1, 0)) +
  scale_y_break(c(stats_breaks[2] + 0.1, stats_breaks[1] - 0.3),
      scales = 0.25, expand = expansion(add = c(0, 0.5)),
      ticklabels = c(signif(stats_breaks[1], digits = 3))) +
  labs(title = "Relative time (Lower is better)") +
  xlab("Benchmark") + ylab("Relative time (Lower=Better)")

if (!is.null(gplt)) {
  ggsave(paste0(paper_plot_path, "geomean_slowdown_16thread.pdf"), plot = gplt, onefile = FALSE, width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
}
oplt <- gplt
gplt <- NULL
oplt
```

#### Thread scaling
```{r latency_rel_t_scaling}
method_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, nthreads_f, suite) %>% summarise(slowdown = exp(mean(log(med_us / clang_1t_us), na.rm = TRUE)))
# ymin = latency_us_q1*plot_scale, , ymax = latency_us_q3*plot_scale
stats_breaks = sort(method_stats$slowdown, decreasing=TRUE)
gplt <- ggplot(method_stats,
    aes(x = interaction(suite, bounds), y = slowdown, group = nthreads_f)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  theme(legend.position = "top") +
  geom_col(aes(fill = nthreads_f), position='dodge') +
  geom_hline(aes(yintercept = 1.0)) +
  scale_y_continuous(breaks = pretty_breaks(n=10)) +
  scale_y_break(c(stats_breaks[4] + 0.1, stats_breaks[3] - 0.3),
      scales = 0.25, expand = expansion(add = c(0, 0.5)),
      ticklabels = c(signif(stats_breaks[1], digits = 2), signif(stats_breaks[3], digits = 2))) +
  labs(title = "Relative slowdown (Lower is better)", fill="Threads") +
  xlab("Benchmark") + ylab("Relative time vs native clang (Lower=Better)")

if (!is.null(gplt)) {
  ggsave(paste0(paper_plot_path, "geomean_slowdown_per_threads.pdf"), plot = gplt, onefile = FALSE, width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
}
oplt <- gplt
gplt <- NULL
oplt
```

## VM comparison
### Geometric average across all benchmarks for the default bounds checking method
```{r vm_default_comp}
vm_stats <- t_info %>% filter(benchname != 'noopbench', is_default_bounds == TRUE) %>%
  group_by(runner, bounds, nthreads_f) %>% summarise(slowdown = exp(mean(log(med_us / clang_1t_us), na.rm = TRUE)))
stats_breaks = sort(vm_stats$slowdown, decreasing=TRUE)
# ymin = latency_us_q1*plot_scale, , ymax = latency_us_q3*plot_scale
gplt <- ggplot(vm_stats,
    aes(x = runner, y = slowdown, group = nthreads_f)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(fill = nthreads_f), position='dodge') +
  geom_hline(aes(yintercept = 1.0)) +
  scale_y_continuous(breaks = pretty_breaks(n=10)) +
  scale_y_break(c(stats_breaks[4] + 0.1, stats_breaks[3] - 0.3),
      scales = 0.25, expand = expansion(add = c(0, 0.5)),
      ticklabels = c(signif(stats_breaks[1], digits = 3), signif(stats_breaks[2], digits = 3), signif(stats_breaks[3], digits = 3))) +
  labs(title = "Relative slowdown (Lower is better)", fill="# of threads") +
  xlab("Benchmark") + ylab("Geometric mean slowdown (Lower=Better)")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "geomean_vm_speed_per_thread.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

### Geometric average across all benchmarks for the default bounds checking method - 1 thread
```{r vm_default_comp_1t}
vm_stats <- t_info %>% filter(benchname != 'noopbench', is_default_bounds == TRUE, nthreads==1) %>%
  group_by(runner, bounds, suite) %>% summarise(slowdown = exp(mean(log(med_us / clang_us), na.rm = TRUE)))
stats_breaks = sort(vm_stats$slowdown, decreasing=TRUE)
# ymin = latency_us_q1*plot_scale, , ymax = latency_us_q3*plot_scale
gplt <- ggplot(vm_stats,
    aes(x = interaction(runner, suite), y = slowdown, fill = runner)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(position='dodge', show.legend = FALSE) +
  geom_hline(aes(yintercept = 1.0)) +
  scale_y_continuous(breaks = pretty_breaks(n=10), expand=c(0.1, 0)) +
  scale_y_break(c(stats_breaks[2] + 0.1, stats_breaks[1] - 0.3),
      scales = 0.25, expand = expansion(add = c(0, 0.5)),
      ticklabels = c(signif(stats_breaks[1], digits = 3))) +
  geom_text(aes(label = sprintf("%.2f%%", slowdown*100), y = pmax(slowdown, 1)), hjust = 0.5, vjust = -1, show.legend = FALSE, nudge_y = 0.01) +
  labs(title = "Relative slowdown (Lower is better)", fill="# of threads") +
  xlab("Benchmark") + ylab("Geometric mean slowdown (Lower=Better)")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "geomean_vm_speed_per_thread_1t.pdf"), width=paper_plot_w_narrow, height=paper_plot_h_narrow, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

## CPU analysis

### Load 1 thread
```{r cpums_load}
cpu_stats <- t_info %>% filter(benchname != 'noopbench', nthreads == 1) %>%
  group_by(runner, bounds, suite) %>% summarise(cpupct = exp(mean(log(
    1600.0*(local_cpums_user_sum + local_cpums_nice_sum + local_cpums_system_sum + local_cpums_irq_sum + local_cpums_softirq_sum)/(total_cpums)
  ),na.rm=TRUE)))
gplt <- ggplot(cpu_stats,
    aes(x = interaction(suite, bounds), fill = bounds, group = bounds)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = cpupct), position = position_dodge2(preserve = "single"), show.legend = FALSE) +
  geom_hline(yintercept = 0.0) +
  geom_hline(yintercept = 100.0) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 1)) +
  labs(title = "CPU load", color = "% NDP", shape = "% NDP", linetype = "Node") +
  xlab("VM Configuration") + ylab("CPU utilization (100%=1 core)")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "cpu_load_mean_1t.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

### Load 16 threads
```{r cpums_load_16t, eval=has_16t}
cpu_stats <- t_info %>% filter(benchname != 'noopbench', nthreads == 16) %>%
  group_by(runner, bounds, suite) %>% summarise(cpupct = exp(mean(log(
    1600.0*(local_cpums_user_sum + local_cpums_nice_sum + local_cpums_system_sum + local_cpums_irq_sum + local_cpums_softirq_sum)/(total_cpums)), na.rm=TRUE
  )))
gplt <- ggplot(cpu_stats,
    aes(x = interaction(suite, bounds), fill = bounds, group = bounds)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = cpupct), position = position_dodge2(preserve = "single"), show.legend = FALSE) +
  geom_hline(yintercept = 1600.0) +
  geom_hline(yintercept = 100.0) +
  geom_hline(yintercept = 0.0) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 1)) +
  labs(title = "CPU load", color = "% NDP", shape = "% NDP", linetype = "Node") +
  xlab(element_blank()) + ylab("CPU utilisation (%)")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "cpu_load_mean_16t.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

### Load 1, 4 and 16 threads
```{r cpums_load_pert}
cpu_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, suite, nthreads_f) %>% summarise(cpupct = exp(mean(log(
    100.0*16.0*(local_cpums_user_sum + local_cpums_nice_sum + local_cpums_system_sum + local_cpums_irq_sum + local_cpums_softirq_sum)/(total_cpums)
  ),na.rm = TRUE)))
gplt <- ggplot(cpu_stats,
    aes(x = interaction(suite, bounds), fill = nthreads_f, group = nthreads_f)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = cpupct), position = 'dodge') +
  geom_hline(yintercept = 100.0) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 1)) +
  labs(title = "CPU load", fill="# of threads") +
  xlab("VM Configuration") + ylab("CPU utilization (100%=all requestsed cores)")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "cpu_load_mean_per_t.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```


### Kernel average RUNNING threads
```{r plot_krunning}
running_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, nthreads_f) %>% summarise(runthreads = mean(
    local_procs_running_avg, na.rm = TRUE
  ))
gplt <- ggplot(running_stats,
    aes(x = bounds, fill = nthreads_f, group = nthreads_f)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = runthreads), position = 'dodge') +
  geom_hline(yintercept = 1.0) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 0.1)) +
  labs(title = "CPU load", fill="# of threads") +
  xlab("VM Configuration") + ylab("Kernel RUNNING threads per requested thread")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "kernel_running_threads_per_nthreads.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

### Context switches 1, 4 and 16 threads
```{r plot_cpu_cswitches}
cswitch_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, nthreads_f, suite) %>% summarise(runthreads = exp(mean(log(
    local_cswitches_sum * 1000 / total_cpums), na.rm = TRUE
  )))
gplt <- ggplot(cswitch_stats,
    aes(x = interaction(suite, bounds), fill = nthreads_f, group = nthreads_f)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  theme(legend.position = "top") +
  geom_col(aes(y = runthreads), position = 'dodge') +
  scale_y_log10(label = scales::label_comma(accuracy = 1)) +
  labs(title = "CPU load", fill = "Threads") +
  xlab("VM Configuration") + ylab("Context switches per CPU second")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "kernel_cswitches_per_s.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

### CPU Migrations per CPU second
```{r plot_cpu_migrations_per_s}
migration_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, suite) %>% summarise(runthreads = mean(
    local_event_cpu_migrations_max * 1000 / total_cpums, na.rm=TRUE
  ))
gplt <- ggplot(migration_stats,
    aes(x = bounds, fill = bounds, group = bounds, color = suite)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = runthreads), position = position_dodge2(preserve = "single")) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 0.1)) +
  labs(title = "CPU migrations", fill = "Bounds") +
  xlab(element_blank()) + ylab("Migrations between CPUs per CPU second")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "kernel_cpu_migrations_per_s.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

### Average memory usage

```{r plot_peak_mem}
mem_stats <- t_info %>% filter(benchname != 'noopbench', nthreads == 1) %>%
  group_by(runner, bounds, suite) %>% summarise(peakmem = exp(mean(log(
    (as.double(local_mem_total - local_mem_available_avg)) / (1024*1024*1024)), na.rm=TRUE
  )))
gplt <- ggplot(mem_stats,
    aes(x = interaction(suite, bounds), fill = bounds, group = bounds)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  theme(legend.position = "top") +
  geom_col(aes(y = peakmem), position = position_dodge2(preserve = "single")) +
  scale_y_log10(breaks = breaks_log(n=10)) +
  labs(fill = "Bounds") +
  xlab(element_blank()) + ylab("Average memory usage [GB]")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "kernel_average_mem_use_polybenchc.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

### CPU Counters

```{r plot_cache_miss_rate}
mem_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, suite) %>% summarise(cpucnt = mean(
    as.double(local_event_cache_accesses_max - local_event_cache_misses_max) / as.double(local_event_cache_accesses_max), na.rm=TRUE
  ))
gplt <- ggplot(mem_stats,
    aes(x = bounds, fill = bounds, group = bounds, color = suite)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = cpucnt), position = position_dodge2(preserve = "single")) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 0.01)) +
  labs(title = "Cache hit rate", fill = "Bounds") +
  xlab(element_blank()) + ylab("Cache hit rate")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "perf_cache_hit_rate.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

```{r plot_branch_hit_rate}
mem_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, suite) %>% summarise(cpucnt = mean(
    as.double(local_event_branches_max - local_event_branch_misses_max) / as.double(local_event_branches_max), na.rm=TRUE
  ))
gplt <- ggplot(mem_stats,
    aes(x = bounds, fill = bounds, group = bounds, color = suite)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  coord_cartesian(ylim = c(0.9, 1)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = cpucnt), position = position_dodge2(preserve = "single")) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 0.01)) +
  labs(title = "Branch prediction rate", fill = "Bounds") +
  xlab(element_blank()) + ylab("Branch prediction rate")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "perf_branch_hit_rate.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

```{r plot_cpi}
mem_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, suite) %>% summarise(cpucnt = mean(
    as.double(local_event_cycles_max) / as.double(local_event_instructions_max), na.rm=TRUE
  ))
gplt <- ggplot(mem_stats,
    aes(x = bounds, fill = bounds, group = bounds, color = suite)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = cpucnt), position = position_dodge2(preserve = "single")) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 0.01)) +
  labs(fill = "Bounds") +
  xlab(element_blank()) + ylab("CPI")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "perf_cpi.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

```{r plot_pagefaults}
mem_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, suite) %>% summarise(cpucnt = mean(
    as.double(local_event_page_faults_max) * 1000 / total_cpums, na.rm=TRUE
  ))
gplt <- ggplot(mem_stats,
    aes(x = bounds, fill = bounds, group = bounds, color = suite)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = cpucnt), position = position_dodge2(preserve = "single")) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 0.01)) +
  labs(fill = "Bounds") +
  xlab(element_blank()) + ylab("Page faults / second")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "perf_pagefaults.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

```{r plot_tlb_hit_rate}
mem_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, suite) %>% summarise(cpucnt = mean(
    as.double(local_event_dtlb_accesses_max + local_event_itlb_accesses_max - local_event_dtlb_misses_max - local_event_itlb_misses_max)
      /
    as.double(local_event_dtlb_accesses_max + local_event_itlb_accesses_max), na.rm=TRUE
  ))
gplt <- ggplot(mem_stats,
    aes(x = bounds, fill = bounds, group = bounds, color = suite)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  coord_cartesian(ylim = c(0.9, 1)) +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = cpucnt), position = position_dodge2(preserve = "single")) +
  scale_y_continuous(breaks = breaks_pretty(n=10), label = scales::label_comma(accuracy = 0.01)) +
  labs(fill = "Bounds") +
  xlab(element_blank()) + ylab("TLB hit rate")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "perf_tlb_hit_rate.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```

```{r plot_instructions}
mem_stats <- t_info %>% filter(benchname != 'noopbench') %>%
  group_by(runner, bounds, suite) %>% summarise(cpucnt = mean(
    as.double(local_event_instructions_max), na.rm=TRUE
  ))
gplt <- ggplot(mem_stats,
    aes(x = bounds, fill = bounds, group = bounds, color = suite)) +
  facet_grid(~runner, scales = "free_x", space = "free_x") +
  paper_disc_scale + paper_fill_scale + paper_shape_scale + paper_theme +
  geom_col(aes(y = cpucnt), position = position_dodge2(preserve = "single")) +
  scale_y_log10(breaks = log_breaks(n=10)) +
  labs(fill = "Bounds") +
  xlab(element_blank()) + ylab("Instructions")

if (!is.null(gplt)) {
  pdf(paste0(paper_plot_path, "perf_instructions.pdf"), width=paper_plot_w, height=paper_plot_h, useDingbats = FALSE, family = paper_font, pointsize = paper_pointsize)
  plot(gplt)
  dev.off()
}
oplt <- gplt
gplt <- NULL
oplt
```
